Looking for CDI Bias

### 2021-07-02 01-preliminary.Rmd
trying out multipleGroups

sex_group = d_demo$sex

mg1 <- multipleGroup(dat, model = 1, group = sex_group, verbose = FALSE) 
mg2 <- multipleGroup(dat, model = 1, group = sex_group, 
                     invariance = 'slopes', verbose = FALSE)

anova(mg2, mg1)
```

>>>>

sex_group = as.character(d_demo$sex)

# mg1 <- multipleGroup(d_mat, model = 1, group = sex_group, verbose = FALSE) 
# Error: Multiple Group model will not be identified without proper constraints (groups contain missing data patterns where item responses have been completely omitted or, alternatively, the number of categories within each group is not equal to the total number of categories)
mg2 <- multipleGroup(d_mat, model = 1, group = sex_group, technical=list(NCYCLES=1000), 
                     invariance = 'slopes', verbose = T)

m_sc2 <- multipleGroup(d_mat, 1, group = sex_group,
                             invariance=c('slopes', 'intercepts', 'free_var','free_means'))
mod_sc1 <- multipleGroup(d_mat, 1, group = sex_group,  #fixed means
                             invariance=c('slopes', 'intercepts', 'free_var'))
mod_fullconstrain <- multipleGroup(d_mat, 1, group = sex_group,
                             invariance=c('slopes', 'intercepts'))

extract.mirt(mod_fullconstrain, 'time') #time of estimation components

save(file = here("data/eng_wg_sex_slopes_invariant.Rds"), mg2)

anova(m1, mg2) # AIC prefers group model, BIC prefers 2PL
mg2s <- summary(mg2)
fem = mg2s[[1]]$rotF
mal = mg2s[[2]]$rotF

plot(x=fem, y=mal) # slopes are constrained to be the same...
# where are the difficulties? 
```
